	Cite from \url{https://www.monero.how/how-to-buy-monero}.
\subsubsection{Overview}
	The fees involved with purchasing Monero will generally be lower if you can purchase directly on a Monero trading exchange such as Kraken. For large purchases, we recommend using an exchange. It can take a few days to send funds to an exchange and get your identity verified with the exchange. \par
	If you are in a rush to buy Monero to take advantage of a dip in prices and you are able to more rapidly obtain some Bitcoin, then you may prefer to purchase Bitcoin first and then instantly convert your Bitcoin to Monero. You can convert your Bitcoin to Monero either using a BTC/XMR exchange service or a simpler service like shapeshift.io which does not require you to register. To search for a place to buy Bitcoin see this list. \par
	In the future, we expect there to be lots more services available to let you purchase Monero more easily in your own country.\par
	\begin{itemize}
		\item \textbf{BUY MONERO DIRECTLY WITH USD/EUR/GBP/CAD/JPY}
			\begin{itemize}
				\item Kraken: Trading exchange via EUR SEPA, USD/EUR Bank Wire, USD/GBP SEPA and SWIFT, JPY/CAD Bank deposit
				\item Bitfinex: Trading exchange USD
				\item Poloniex: Trading exchange via Tether USD
				\item AnyCoin: EU SEPA transfer
				\item MoneroDirect: OKPAY
				\item LiveCoin: Wire transfer (SWIFT), OKPAY
				\item LiteBit: EU SEPA, Paypal
				\item MoneroForCash: Person-to-person
			\end{itemize}
		\item \textbf{CONVERTING BITCOIN TO AND FROM MONERO}
			\begin{itemize}
				\item Shapeshift.io: No account or registration required
				\item Bitsquare: XMR.to Monero to Bitcoin only
				\item Alfa Cashier: TuxExchange
			\end{itemize}
			In addition to these services, use any of the exchanges listed in the "BTC/XMR Exchanges" section. Shapeshift is the easiest method in our experience, since there is no need to sign up for an account.
		\item \textbf{USD/XMR EXCHANGES}
			\begin{table}[H]
				\centering
				\begin{tabular}{ccc}
					\hline
						&Price	&24hr Volume (XMR)\\
					\hline
					Bitfinex	&50.97	&11,094 \\
					\hline
					Kraken	&51.27	&5,536 \\
					\hline
					Livecoin	&51.60	&279 \\
					\hline
				\end{tabular}
			\end{table}
			Note that Poloniex requires USD Tether coins, and cannot accept USD directly
		\item \textbf{BTC/XMR EXCHANGES}
			\begin{table}[htbp!]
				\centering
				\begin{tabular}{ccc}
					\hline
						&Price	&24hr Volume (XMR) \\
					\hline
					Poloniex	&0.0189	&146,659 \\
					\hline
					Bittrex	&0.0187	&26,573 \\
					\hline
					Kraken	&0.0188	&17,788 \\
					\hline
					BitFinex	&0.0188	&16,482 \\
					\hline
					Livecoin	&0.0183	&10,877 \\
					\hline	
					Bter	&0.0180	&20 \\
					\hline
				\end{tabular}
			\end{table}
	\end{itemize}
	See \href{https://moneroeric.com/buy-monero-bitcoin-shapeshift-poloniex/}{MoneroEric's guide} on purchasing Monero via Poloniex and for swapping Bitcoin for Monero with shapeshift.io.
